\pkg{DNest4}: An implementation of Diffusive Nested Sampling in \proglang{C++11} and \proglang{Python}

### 2016-05-10 paper/ms.tex
Bye bye minted

\documentclass[article]{jss}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{dsfont}
\usepackage{minted}

@@

\begin{minted}[mathescape,
               numbersep=5pt,
               gobble=0,
               frame=single,
               framesep=2mm, fontsize=\small]{c++}
void StraightLine::from_prior(RNG& rng)
{
    // Naive diffuse prior
    m = 1E3*rng.randn();
    b = 1E3*rng.randn();

    // Log-uniform prior
    sigma = exp(-10. + 20.*rng.rand());

    // Compute the model line
    calculate_mu();
}
\end{minted}

\begin{minted}[mathescape,
               numbersep=5pt,
               gobble=0,
               frame=single,
               framesep=2mm, fontsize=\small]{c++}
double StraightLine::perturb(RNG& rng)
{
    double log_H = 0.;

    // Proposals explore the prior
    // For normal priors I usually use the hastings factor to do it
    int which = rng.rand_int(3);
    if(which == 0)
    {
        log_H -= -0.5*pow(m/1E3, 2);
        m += 1E3*rng.randh();
        log_H += -0.5*pow(m/1E3, 2);
    }
    else if(which == 1)
    {
        log_H -= -0.5*pow(b/1E3, 2);
        b += 1E3*rng.randh();
        log_H += -0.5*pow(b/1E3, 2);
    }
    else
    {
        // Usual log-uniform prior trick
        sigma = log(sigma);
        sigma += 20.*rng.randh();
        wrap(sigma, -10., 10.);
        sigma = exp(sigma);
    }

    // Calculate mu again if m or b changed
    if(which == 0 || which == 1)
        calculate_mu();

    return log_H;
}
\end{minted}

>>>>

\documentclass[article]{jss}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{dsfont}

@@

The member function used to generate straight line parameters from the
prior is:

\begin{CodeChunk}
\begin{CodeInput}
void StraightLine::from_prior(RNG& rng)
{
   // Naive diffuse prior
   m = 1E3*rng.randn();
   b = 1E3*rng.randn();

   // Log-uniform prior
   sigma = exp(-10.0 + 20.0*rng.rand());

   // Compute the model line
   calculate_mu();
}
\end{CodeInput}
\end{CodeChunk}
